---
title: "Assignment_3_Regression"
output:
  pdf_document: default
  html_document: default
  word_document: default
date: "2023-11-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tinytex)
```


#1)Run the following code in R-studio to create two variables X and Y?

```{r}
set.seed(2017)
X=runif(100)*10
Y=X*4+3.45
Y=rnorm(100)*0.29*Y+Y

```

#a)Plot Y against X. Include a screenshot of the plot in your submission. Using the File menu you can save the graph as a picture on your computer. Based on the plot do you think we can fit a linear model to explain Y based on X?

```{r}
plot(X,Y, xlab = "X (units)", ylab = "Y (units)", main = "Plot of Y vs X ", col = "red")
```
##There is a positive linear trend between X variables and Y variables.

#b)Construct a simple linear model of Y based on X. Write the equation that explains Y based on X. What is the accuracy of this model?

```{r}
linearModel <- lm(Y~X)
linearModel$coefficients
```
# c)How the Coefficient of Determination, R 2, of the model above is related to the correlation coefficient of X and Y?
```{r}
summary(linearModel)
```

#2)We will use the ‘mtcars’ dataset for this question. The dataset is already included in your R distribution. The dataset shows some of the characteristics of different cars. The following shows few samples (i.e. the first 6 rows) of the dataset.
```{r}
head(mtcars)
```

#a) James wants to buy a car. He and his friend, Chris, have different opinions about the Horse Power (hp) of cars. James think the weight of a car (wt) can be used to estimate the HorsePower of the car while Chris thinks the fuel consumption expressed in Mile Per Gallon (mpg),is a better estimator of the (hp). Who do you think is right? Construct simple linear models using mtcars data to answer the question.
```{r}
linearmodel2 = lm(hp~wt, data = mtcars)
summary(linearmodel2)
plot(mtcars$wt,mtcars$hp, xlab = "Weight (wt)", ylab = "Horsepower (hp)", main = "Plot of Weight vs Horsepower", col = "blue")
```

```{r}
# Creating a linear model for mpg vs horsepower and displays a plot of the points
linearModel3 = lm(hp~mpg, data = mtcars)
summary(linearModel3)
plot(mtcars$mpg,mtcars$hp, xlab = "Miles per Gallon (mpg)", ylab = "Horsepower (hp)", main = "Plot of Miles Per Gallon vs Horsepower", col = "blue")
```

#b) Build a model that uses the number of cylinders (cyl) and the mile per gallon (mpg) values of a car to predict the car Horse Power (hp). Using this model, what is the estimated Horse Power of a car with 4 calendar and mpg of 22?
```{r}
# Shows which variables are factor or numeric
str(mtcars)
# Converting cylinder into a factor
mtcars$cyl = as.factor(mtcars$cyl)
str(mtcars)
```

```{r}
linearModel4 = lm(hp~cyl+mpg, data = mtcars)
summary(linearModel4)
# Predict the estimated horse power of a car with 4 cylinders and 22 mpg
predict(linearModel4, data.frame(mpg = c(22), cyl = c("4")))
```
#With four calendar months and 22 mpg, the estimated horsepower of the car is 98.15%.

#3) Using BostonHousing Dataset
```{r}
library(mlbench)
data(BostonHousing)
```

#a)Build a model to estimate the median value of owner-occupied homes (medv)based on the following variables: crime crate (crim), proportion of residential land zoned for lots over 25,000 sq.ft (zn), the local pupil-teacher ratio (ptratio) and weather the whether the tractbounds Chas River(chas). Is this an accurate model?
```{r}
str(BostonHousing)
```

```{r}
# Creating a linear model for median value based on crim, zn, ptratio, and chas.
linearModel5 = lm(medv~crim+zn+ptratio+chas, data = BostonHousing)
summary(linearModel5)
```
This model's (crim, zn, ptratio, and chas) R2 value is 35.99% of the variance in the median home value. The accuracy of this model is poor, and it might be strengthened by including more variables.

#b)Use the estimated coefficient to answer these questions?
#I. Imagine two houses that are identical in all aspects but one bounds the Chas River and the other does not. Which one is more expensive and by how much?
Based on the coefficients, the resulting formula from our model is:-medv = 49.91868 - 0.26018*crim + 0.07073*zn - 1.49367*ptratio + 4.58393*chas1.

Therefore, if the only difference between two houses is that one borders the Chas River, then we focus on the chas variable coefficient. The house that borders the river would be $4,583.93 more than the one that does not.
4.58393 (coeff of chas) * 1 (value of chas) * 1000 (medv in $1,000 units) = $4,583.93
Based on the coefficients, the resulting formula from our model is:
medv = 49.91868 - 0.26018*crim + 0.07073*zn - 1.49367*ptratio + 4.58393*chas1.

Thus, we concentrate on the ptratio variable coefficient if the pupil-teacher ratio is the only distinction between two houses. The dwelling with the lower pupil-teacher ratio number is therefore more costly, as our model's coefficient turns out to be negative. The houses' valuations diverge to the extent that

-1.49367 (coeff of ptratio) * 0.03 (difference between ptratio values) * 1000 (medv in $1,000 units) = $44.81

According to our calculations, the home with the lower student-teacher ratio is therefore $44.81 more expensive.

#c)Which of the variables are statistically important (i.e. related to the house price)? Hint: use the p-values of the coefficients to answer. 

All of the variables—crim, zn, ptratio, and chas—were determined to be statistically significant based on the model built using these data. 
This is confirmed by the fact that every p-value derived from our model was less than the significance threshold of 0.05.

#d)Use the anova analysis and determine the order of importance of these four variables.
```{r}
anova(linearModel5)
```
Based on the returned ANOVA values we can determine the order of importance, for these variables;

1. The variable "crim" explains 15.08% of the variability in the model.
2. Following that the variable "ptratio" accounts for 11.02% of the models variability.
3. The "zn" variable contributes 8.32% to the models variability.
4. Lastly we have the "variable, which explains 1.56% of the models variability.

Despite these findings it is important to note that residuals still account for a portion (around 64.01%) of variability within this model. This suggests that there is room for improvement, in terms of accuracy.


